---
title: "Weeks 5-7"
author: "Ezinne Nwankwo"
date: "7/23/2019"
output: html_document
---

```{r libraries}

library(dplyr)
library(purrr)
library(tidyverse)
library(ggplot2)
#install.packages("repurrrsive")
library(repurrrsive)

```


## Exercise 1 

```{r}

movies = readr::read_csv("https://www.stat.duke.edu/~cr173/Sta523_Fa18/slides/data/movies/movies.csv") 
movies

ggplot(data = movies, aes(x = imdb_num_votes, y = imdb_rating, color = audience_rating)) + 
  geom_point(alpha = 0.5) + 
  theme_bw() +
  facet_wrap(~ mpaa_rating) + 
  labs(x = "IMDB number of votes", y = "IMDB rating", color = "Audience rating", 
    title = "IMDB and RT scores, by MPAA rating") 

  
```

## Exercise 2 

```{r}

ggplot(data = movies, aes(x = audience_score, y = critics_score, color = best_pic_nom)) + 
  geom_point() + 
  theme_bw() + 
  facet_wrap( ~ mpaa_rating) + 
  geom_smooth(method = "lm", color = "black", se = FALSE, fullrange = TRUE) + 
  geom_abline(intercept = 0, slope = 1, color = "gray")
```



## Homework 3 

```{r}


sales = readRDS("lego_sales.rds")
#View(sales)
str(sales)

## Creating a dataframe

fix_phone_num <- function(v){
  
}

tidy_sales = data_frame(
  first_name = map_chr(sales, "first_name"),
  last_name = map_chr(sales, "last_name"),
  gender = map_chr(sales, "gender"), 
  age = map_chr(sales, "age") %>% as.integer(), 
  phone_number = map_chr(sales, "phone_number", .default = NA), 
  hobbies = map(sales, "hobbies"), 
  purchases = map(sales, "purchases")
) %>% 
  mutate(
    no_hobbies = map_int(hobbies, length),
    no_purchases = map_int(purchases, length)
  ) 



``` 

1. What are the three most common first names of purchasers?
```{r}

tidy_sales %>% count(first_name, sort = TRUE) %>% top_n(3, n)

```
  
  
2. What are the five most popular lego sets based on these data?

```{r}

tidy_sales %>% tidyr::unnest(purchases = purchases) 

```

  
  
  
  .. .. ..$ Number  : chr "70595"
  .. .. ..$ Theme   : chr "Ninjago"
  .. .. ..$ Subtheme: chr "Rise of the Villains"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Ultra Stealth Raider"
  .. .. ..$ Pieces  : int 1093
  .. .. ..$ USPrice : num 120
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70595-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24721
  .. .. ..$ Number  : chr "10831"
  .. .. ..$ Theme   : chr "Duplo"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "My First Caterpillar"
  .. .. ..$ Pieces  : int 19
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/10831-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 6
  ..$ gender    : chr "Female"
  ..$ first_name: chr "Bryanna"
  ..$ last_name : chr "Welsh"
  ..$ age       : num 19
  ..$ hobbies   : chr [1:2] "Animal fancy" "Sand art"
  ..$ purchases :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24797
  .. .. ..$ Number  : chr "75138"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "Episode V"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Hoth Attack"
  .. .. ..$ Pieces  : int 233
  .. .. ..$ USPrice : num 25
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75138-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24701
  .. .. ..$ Number  : chr "76062"
  .. .. ..$ Theme   : chr "DC Comics Super Heroes"
  .. .. ..$ Subtheme: chr "Mighty Micros"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Robin vs. Bane"
  .. .. ..$ Pieces  : int 77
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/76062-1.jpg"
  .. .. ..$ Quantity: num 3
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Caleb"
  ..$ last_name   : chr "Garcia-Wideman"
  ..$ age         : num 37
  ..$ phone_number: chr "907-555-9236"
  ..$ hobbies     : chr [1:3] "Pet" "Skateboarding" "Jigsaw puzzles"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24730
  .. .. ..$ Number  : chr "41115"
  .. .. ..$ Theme   : chr "Friends"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Emma's Creative Workshop"
  .. .. ..$ Pieces  : int 108
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41115-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25611
  .. .. ..$ Number  : chr "21127"
  .. .. ..$ Theme   : chr "Minecraft"
  .. .. ..$ Subtheme: chr "Minifig-scale"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "The Fortress"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 110
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/21127-1.jpg"
  .. .. ..$ Quantity: num 2
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Chase"
  ..$ last_name   : chr "Fortenberry"
  ..$ age         : num 19
  ..$ phone_number: chr "205-555-3704"
  ..$ hobbies     : chr [1:2] "Birdwatching" "Dog sport"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24707
  .. .. ..$ Number  : chr "10801"
  .. .. ..$ Theme   : chr "Duplo"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Baby Animals"
  .. .. ..$ Pieces  : int 13
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/10801-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24713
  .. .. ..$ Number  : chr "10809"
  .. .. ..$ Theme   : chr "Duplo"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Police Patrol"
  .. .. ..$ Pieces  : int 15
  .. .. ..$ USPrice : num 15
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/10809-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Kevin"
  ..$ last_name   : chr "Cruz"
  ..$ age         : num 20
  ..$ phone_number: chr "947-555-7946"
  ..$ hobbies     : chr "Gunsmithing"
  ..$ purchases   :List of 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24767
  .. .. ..$ Number  : chr "70335"
  .. .. ..$ Theme   : chr "Nexo Knights"
  .. .. ..$ Subtheme: chr "Ultimate"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Ultimate Lavaria"
  .. .. ..$ Pieces  : int 69
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70335-1.jpg"
  .. .. ..$ Quantity: num 2
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Connor"
  ..$ last_name   : chr "Brown"
  ..$ age         : num 36
  ..$ phone_number: chr "516-555-4310"
  ..$ hobbies     : chr "Dance"
  ..$ purchases   :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24548
  .. .. ..$ Number  : chr "71230"
  .. .. ..$ Theme   : chr "Dimensions"
  .. .. ..$ Subtheme: chr "Fun Pack"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Fun Pack: Doc Brown"
  .. .. ..$ Pieces  : int 69
  .. .. ..$ USPrice : num 15
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/71230-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24913
  .. .. ..$ Number  : chr "60112"
  .. .. ..$ Theme   : chr "City"
  .. .. ..$ Subtheme: chr "Fire"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Fire Engine"
  .. .. ..$ Pieces  : int 376
  .. .. ..$ USPrice : num 50
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/60112-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 26034
  .. .. ..$ Number  : chr "41573"
  .. .. ..$ Theme   : chr "Mixels"
  .. .. ..$ Subtheme: chr "Series 9"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Sweepz"
  .. .. ..$ Pieces  : int 61
  .. .. ..$ USPrice : num 4.99
  .. .. ..$ ImageURL: chr ""
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Toni"
  ..$ last_name   : chr "Borison"
  ..$ age         : num 40
  ..$ phone_number: chr "284-555-4560"
  ..$ hobbies     : chr [1:2] "Singing" "Dowsing"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25626
  .. .. ..$ Number  : chr "70595"
  .. .. ..$ Theme   : chr "Ninjago"
  .. .. ..$ Subtheme: chr "Rise of the Villains"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Ultra Stealth Raider"
  .. .. ..$ Pieces  : int 1093
  .. .. ..$ USPrice : num 120
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70595-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24994
  .. .. ..$ Number  : chr "10251"
  .. .. ..$ Theme   : chr "Advanced Models"
  .. .. ..$ Subtheme: chr "Modular Buildings"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Brick Bank"
  .. .. ..$ Pieces  : int 2380
  .. .. ..$ USPrice : num 170
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/10251-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Daniel"
  ..$ last_name   : chr "Hurst"
  ..$ age         : num 44
  ..$ phone_number: chr "251-555-0845"
  ..$ hobbies     : chr "Crossword puzzles"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24903
  .. .. ..$ Number  : chr "41558"
  .. .. ..$ Theme   : chr "Mixels"
  .. .. ..$ Subtheme: chr "Series 7"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Mixadel"
  .. .. ..$ Pieces  : int 63
  .. .. ..$ USPrice : num 4.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41558-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24695
  .. .. ..$ Number  : chr "31048"
  .. .. ..$ Theme   : chr "Creator"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Lakeside Lodge"
  .. .. ..$ Pieces  : int 368
  .. .. ..$ USPrice : num 30
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/31048-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Judith"
  ..$ last_name   : chr "Webb"
  ..$ age         : num 39
  ..$ phone_number: chr "917-555-7417"
  ..$ hobbies     : chr [1:3] "Beach Volleyball" "Bowling" "Netball"
  ..$ purchases   :List of 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 26058
  .. .. ..$ Number  : chr "5005059"
  .. .. ..$ Theme   : chr "Gear"
  .. .. ..$ Subtheme: chr "Video Games/PS3"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Marvel Avengers PS3 Video Game"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 50
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/5005059-1.jpg"
  .. .. ..$ Quantity: num 2
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Nicholas"
  ..$ last_name   : chr "Belfageoua"
  ..$ age         : num 46
  ..$ phone_number: chr "606-555-4814"
  ..$ hobbies     : chr "Bodybuilding"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25881
  .. .. ..$ Number  : chr "853549"
  .. .. ..$ Theme   : chr "Gear"
  .. .. ..$ Subtheme: chr "Key Chains/Friends"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Mia Key Chain"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 5.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/853549-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25642
  .. .. ..$ Number  : chr "70327"
  .. .. ..$ Theme   : chr "Nexo Knights"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "The King's Mech"
  .. .. ..$ Pieces  : int 375
  .. .. ..$ USPrice : num 30
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70327-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Amanda"
  ..$ last_name   : chr "Tronnier"
  ..$ age         : num 45
  ..$ phone_number: chr "317-555-7477"
  ..$ hobbies     : chr [1:2] "Topiary" "Baseball"
  ..$ purchases   :List of 4
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24959
  .. .. ..$ Number  : chr "75139"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "The Force Awakens"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Battle on Takodana"
  .. .. ..$ Pieces  : int 409
  .. .. ..$ USPrice : num 60
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75139-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25887
  .. .. ..$ Number  : chr "853543"
  .. .. ..$ Theme   : chr "Ninjago"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Ninjago Party Set"
  .. .. ..$ Pieces  : int 70
  .. .. ..$ USPrice : num 7.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/853543-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24685
  .. .. ..$ Number  : chr "60118"
  .. .. ..$ Theme   : chr "City"
  .. .. ..$ Subtheme: chr "Traffic"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Garbage Truck"
  .. .. ..$ Pieces  : int 248
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/60118-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25901
  .. .. ..$ Number  : chr "5004612"
  .. .. ..$ Theme   : chr "Gear"
  .. .. ..$ Subtheme: chr "Watches/Clocks"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Lucy Wyldstyle Minifigure Link Watch"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 25
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/5004612-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Jacob"
  ..$ last_name   : chr "Nzabanita"
  ..$ age         : num 31
  ..$ phone_number: chr "339-555-2572"
  ..$ hobbies     : chr "Orienteering"
  ..$ purchases   :List of 4
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24732
  .. .. ..$ Number  : chr "41117"
  .. .. ..$ Theme   : chr "Friends"
  .. .. ..$ Subtheme: chr "Pop Star"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Pop Star TV Studio"
  .. .. ..$ Pieces  : int 194
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41117-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24793
  .. .. ..$ Number  : chr "75133"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "Battlefront"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Rebel Alliance Battle Pack"
  .. .. ..$ Pieces  : int 101
  .. .. ..$ USPrice : num 13
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75133-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24723
  .. .. ..$ Number  : chr "41172"
  .. .. ..$ Theme   : chr "Elves"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "The Water Dragon Adventure"
  .. .. ..$ Pieces  : int 212
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41172-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25920
  .. .. ..$ Number  : chr "75151"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "Episode III"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Clone Turbo Tank"
  .. .. ..$ Pieces  : int 903
  .. .. ..$ USPrice : num 110
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75151-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Hannah"
  ..$ last_name   : chr "Drews Stunkel"
  ..$ age         : num 55
  ..$ phone_number: chr "339-555-6320"
  ..$ hobbies     : chr "Shortwave listening"
  ..$ purchases   :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25628
  .. .. ..$ Number  : chr "70590"
  .. .. ..$ Theme   : chr "Ninjago"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Airjitzu Battle Grounds"
  .. .. ..$ Pieces  : int 666
  .. .. ..$ USPrice : num 60
  .. .. ..$ ImageURL: chr ""
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25624
  .. .. ..$ Number  : chr "70593"
  .. .. ..$ Theme   : chr "Ninjago"
  .. .. ..$ Subtheme: chr "Skybound"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "The Green NRG Dragon"
  .. .. ..$ Pieces  : int 567
  .. .. ..$ USPrice : num 50
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70593-1.jpg"
  .. .. ..$ Quantity: num 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24734
  .. .. ..$ Number  : chr "41119"
  .. .. ..$ Theme   : chr "Friends"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Heartlake Cupcake Cafe"
  .. .. ..$ Pieces  : int 439
  .. .. ..$ USPrice : num 40
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41119-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 6
  ..$ gender    : chr "Male"
  ..$ first_name: chr "Erik"
  ..$ last_name : chr "Brownrigg"
  ..$ age       : num 44
  ..$ hobbies   : chr [1:2] "Kombucha Brewing" "Martial arts"
  ..$ purchases :List of 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25621
  .. .. ..$ Number  : chr "70589"
  .. .. ..$ Theme   : chr "Ninjago"
  .. .. ..$ Subtheme: chr "Rise of the Villains"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Rock Roader"
  .. .. ..$ Pieces  : int 406
  .. .. ..$ USPrice : num 40
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70589-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Jackson"
  ..$ last_name   : chr "Martinez"
  ..$ age         : num 43
  ..$ phone_number: chr "250-555-1732"
  ..$ hobbies     : chr "People watching"
  ..$ purchases   :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24669
  .. .. ..$ Number  : chr "71304"
  .. .. ..$ Theme   : chr "Bionicle"
  .. .. ..$ Subtheme: chr "Companions"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Terak - Creature of Earth"
  .. .. ..$ Pieces  : int 74
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/71304-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24904
  .. .. ..$ Number  : chr "41559"
  .. .. ..$ Theme   : chr "Mixels"
  .. .. ..$ Subtheme: chr "Series 7"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Paladum"
  .. .. ..$ Pieces  : int 64
  .. .. ..$ USPrice : num 4.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41559-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24665
  .. .. ..$ Number  : chr "21031"
  .. .. ..$ Theme   : chr "Architecture"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Burj Khalifa"
  .. .. ..$ Pieces  : int 333
  .. .. ..$ USPrice : num 40
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/21031-1.jpg"
  .. .. ..$ Quantity: num 3
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Riley"
  ..$ last_name   : chr "Ott"
  ..$ age         : num 51
  ..$ phone_number: chr "517-555-2093"
  ..$ hobbies     : chr [1:2] "Quilting" "Driving"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24785
  .. .. ..$ Number  : chr "75126"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "MicroFighters"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "First Order Snowspeeder"
  .. .. ..$ Pieces  : int 91
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75126-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24772
  .. .. ..$ Number  : chr "70604"
  .. .. ..$ Theme   : chr "Ninjago"
  .. .. ..$ Subtheme: chr "Skybound"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Tiger Widow Island"
  .. .. ..$ Pieces  : int 450
  .. .. ..$ USPrice : num 50
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70604-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Hector"
  ..$ last_name   : chr "Collins"
  ..$ age         : num 20
  ..$ phone_number: chr "340-555-2508"
  ..$ hobbies     : chr "Kart racing"
  ..$ purchases   :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24781
  .. .. ..$ Number  : chr "75116"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "Buildable Figures"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Finn"
  .. .. ..$ Pieces  : int 98
  .. .. ..$ USPrice : num 25
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75116-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24723
  .. .. ..$ Number  : chr "41172"
  .. .. ..$ Theme   : chr "Elves"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "The Water Dragon Adventure"
  .. .. ..$ Pieces  : int 212
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41172-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24627
  .. .. ..$ Number  : chr "75098"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "Ultimate Collector Series"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Assault on Hoth"
  .. .. ..$ Pieces  : int 2144
  .. .. ..$ USPrice : num 250
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75098-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Mckenzie"
  ..$ last_name   : chr "Cherry"
  ..$ age         : num 37
  ..$ phone_number: chr "336-555-9269"
  ..$ hobbies     : chr [1:3] "Archery" "Calligraphy" "Dancing"
  ..$ purchases   :List of 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25878
  .. .. ..$ Number  : chr "853505"
  .. .. ..$ Theme   : chr "Gear"
  .. .. ..$ Subtheme: chr "Role-Play toys"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "NK Sword Standard"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/853505-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 6
  ..$ gender    : chr "Female"
  ..$ first_name: chr "Michelle"
  ..$ last_name : chr "Uguccioni"
  ..$ age       : num 17
  ..$ hobbies   : chr [1:3] "Rugby" "Topiary" "Metalworking"
  ..$ purchases :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24756
  .. .. ..$ Number  : chr "70310"
  .. .. ..$ Theme   : chr "Nexo Knights"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Knighton Battle Blaster"
  .. .. ..$ Pieces  : int 76
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70310-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24896
  .. .. ..$ Number  : chr "31046"
  .. .. ..$ Theme   : chr "Creator"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Fast Car"
  .. .. ..$ Pieces  : int 222
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/31046-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Rebecca"
  ..$ last_name   : chr "Duval"
  ..$ age         : num 48
  ..$ phone_number: chr "908-555-4029"
  ..$ hobbies     : chr [1:2] "Video gaming" "Triathlon"
  ..$ purchases   :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24899
  .. .. ..$ Number  : chr "41114"
  .. .. ..$ Theme   : chr "Friends"
  .. .. ..$ Subtheme: chr "Party"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Party Styling"
  .. .. ..$ Pieces  : int 54
  .. .. ..$ USPrice : num 4.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41114-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 26034
  .. .. ..$ Number  : chr "41573"
  .. .. ..$ Theme   : chr "Mixels"
  .. .. ..$ Subtheme: chr "Series 9"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Sweepz"
  .. .. ..$ Pieces  : int 61
  .. .. ..$ USPrice : num 4.99
  .. .. ..$ ImageURL: chr ""
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24664
  .. .. ..$ Number  : chr "21028"
  .. .. ..$ Theme   : chr "Architecture"
  .. .. ..$ Subtheme: chr "Skylines"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "New York City"
  .. .. ..$ Pieces  : int 598
  .. .. ..$ USPrice : num 60
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/21028-1.jpg"
  .. .. ..$ Quantity: num 2
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Katherine"
  ..$ last_name   : chr "Hogue"
  ..$ age         : num 27
  ..$ phone_number: chr "289-555-4928"
  ..$ hobbies     : chr [1:2] "Meteorology" "Roller derby"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25876
  .. .. ..$ Number  : chr "853555"
  .. .. ..$ Theme   : chr "Gear"
  .. .. ..$ Subtheme: chr "Stationery"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Campsite Scrapbook"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 15
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/853555-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25660
  .. .. ..$ Number  : chr "75822"
  .. .. ..$ Theme   : chr "The Angry Birds Movie"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Piggy Plane Attack"
  .. .. ..$ Pieces  : int 168
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75822-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Adoria"
  ..$ last_name   : chr "Hammond"
  ..$ age         : num 40
  ..$ phone_number: chr "712-555-6781"
  ..$ hobbies     : chr(0) 
  ..$ purchases   :List of 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24720
  .. .. ..$ Number  : chr "10830"
  .. .. ..$ Theme   : chr "Duplo"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Minnie's Café"
  .. .. ..$ Pieces  : int 27
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/10830-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Amanda"
  ..$ last_name   : chr "Musick"
  ..$ age         : num 24
  ..$ phone_number: chr "878-555-7113"
  ..$ hobbies     : chr "Electronics"
  ..$ purchases   :List of 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25916
  .. .. ..$ Number  : chr "76054"
  .. .. ..$ Theme   : chr "DC Comics Super Heroes"
  .. .. ..$ Subtheme: chr "Batman"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Batman: Scarecrow Harvest of Fear"
  .. .. ..$ Pieces  : int 563
  .. .. ..$ USPrice : num 60
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/76054-1.jpg"
  .. .. ..$ Quantity: num 2
 $ :List of 6
  ..$ gender    : chr "Female"
  ..$ first_name: chr "Cecilia"
  ..$ last_name : chr "Mauro"
  ..$ age       : num 50
  ..$ hobbies   : chr [1:2] "Stone skipping" "Kitesurfing"
  ..$ purchases :List of 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25921
  .. .. ..$ Number  : chr "75157"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "Rebels"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Captain Rex's AT-TE"
  .. .. ..$ Pieces  : int 972
  .. .. ..$ USPrice : num 120
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75157-1.jpg"
  .. .. ..$ Quantity: num 3
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Shina"
  ..$ last_name   : chr "Hegarty"
  ..$ age         : num 22
  ..$ phone_number: chr "868-555-1868"
  ..$ hobbies     : chr [1:2] "Singing" "Kitesurfing"
  ..$ purchases   :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24737
  .. .. ..$ Number  : chr "41135"
  .. .. ..$ Theme   : chr "Friends"
  .. .. ..$ Subtheme: chr "Pop Star"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Livi's Pop Star House"
  .. .. ..$ Pieces  : int 597
  .. .. ..$ USPrice : num 50
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41135-1.jpg"
  .. .. ..$ Quantity: num 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24706
  .. .. ..$ Number  : chr "41142"
  .. .. ..$ Theme   : chr "Disney Princess"
  .. .. ..$ Subtheme: chr "Palace Pets"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Palace Pets Royal Castle"
  .. .. ..$ Pieces  : int 186
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41142-1.jpg"
  .. .. ..$ Quantity: num 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24664
  .. .. ..$ Number  : chr "21028"
  .. .. ..$ Theme   : chr "Architecture"
  .. .. ..$ Subtheme: chr "Skylines"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "New York City"
  .. .. ..$ Pieces  : int 598
  .. .. ..$ USPrice : num 60
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/21028-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Anthony"
  ..$ last_name   : chr "Kiyotake"
  ..$ age         : num 22
  ..$ phone_number: chr "980-555-0099"
  ..$ hobbies     : chr "Hunting"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25007
  .. .. ..$ Number  : chr "41568"
  .. .. ..$ Theme   : chr "Mixels"
  .. .. ..$ Subtheme: chr "Series 8"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Lewt"
  .. .. ..$ Pieces  : int 62
  .. .. ..$ USPrice : num 4.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41568-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25883
  .. .. ..$ Number  : chr "853568"
  .. .. ..$ Theme   : chr "Gear"
  .. .. ..$ Subtheme: chr "Key Chains/City"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Prison Guard Key Chain"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 5.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/853568-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Connor"
  ..$ last_name   : chr "Fourzan"
  ..$ age         : num 32
  ..$ phone_number: chr "805-555-3065"
  ..$ hobbies     : chr [1:2] "Billiards" "Speed skating"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25886
  .. .. ..$ Number  : chr "853519"
  .. .. ..$ Theme   : chr "Gear"
  .. .. ..$ Subtheme: chr "Playmats"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "NK Playmat"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 15
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/853519-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24789
  .. .. ..$ Number  : chr "75130"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "MicroFighters"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "AT-DP"
  .. .. ..$ Pieces  : int 76
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75130-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Kayla"
  ..$ last_name   : chr "Rush"
  ..$ age         : num 25
  ..$ phone_number: chr "281-555-9341"
  ..$ hobbies     : chr "Gunsmithing"
  ..$ purchases   :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24896
  .. .. ..$ Number  : chr "31046"
  .. .. ..$ Theme   : chr "Creator"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Fast Car"
  .. .. ..$ Pieces  : int 222
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/31046-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24750
  .. .. ..$ Number  : chr "76065"
  .. .. ..$ Theme   : chr "Marvel Super Heroes"
  .. .. ..$ Subtheme: chr "Mighty Micros"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Captain America vs. Red Skull"
  .. .. ..$ Pieces  : int 95
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/76065-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25662
  .. .. ..$ Number  : chr "75824"
  .. .. ..$ Theme   : chr "The Angry Birds Movie"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Pig City Teardown"
  .. .. ..$ Pieces  : int 386
  .. .. ..$ USPrice : num 40
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75824-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Lucas"
  ..$ last_name   : chr "Montoya"
  ..$ age         : num 34
  ..$ phone_number: chr "616-555-2269"
  ..$ hobbies     : chr [1:3] "Badminton" "Dance" "Soapmaking"
  ..$ purchases   :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24901
  .. .. ..$ Number  : chr "41555"
  .. .. ..$ Theme   : chr "Mixels"
  .. .. ..$ Subtheme: chr "Series 7"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Busto"
  .. .. ..$ Pieces  : int 69
  .. .. ..$ USPrice : num 4.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41555-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24899
  .. .. ..$ Number  : chr "41114"
  .. .. ..$ Theme   : chr "Friends"
  .. .. ..$ Subtheme: chr "Party"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Party Styling"
  .. .. ..$ Pieces  : int 54
  .. .. ..$ USPrice : num 4.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41114-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24762
  .. .. ..$ Number  : chr "70330"
  .. .. ..$ Theme   : chr "Nexo Knights"
  .. .. ..$ Subtheme: chr "Ultimate"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Ultimate Clay"
  .. .. ..$ Pieces  : int 72
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70330-1.jpg"
  .. .. ..$ Quantity: num 2
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Peggy"
  ..$ last_name   : chr "Hiner"
  ..$ age         : num 21
  ..$ phone_number: chr "563-555-1011"
  ..$ hobbies     : chr [1:2] "Flying" "Speed skating"
  ..$ purchases   :List of 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24734
  .. .. ..$ Number  : chr "41119"
  .. .. ..$ Theme   : chr "Friends"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Heartlake Cupcake Cafe"
  .. .. ..$ Pieces  : int 439
  .. .. ..$ USPrice : num 40
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41119-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 6
  ..$ gender    : chr "Female"
  ..$ first_name: chr "Maya"
  ..$ last_name : chr "Wolfe"
  ..$ age       : num 33
  ..$ hobbies   : chr [1:2] "Acting" "Rock balancing"
  ..$ purchases :List of 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25881
  .. .. ..$ Number  : chr "853549"
  .. .. ..$ Theme   : chr "Gear"
  .. .. ..$ Subtheme: chr "Key Chains/Friends"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Mia Key Chain"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 5.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/853549-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Keno"
  ..$ last_name   : chr "Graves"
  ..$ age         : num 51
  ..$ phone_number: chr "209-555-6030"
  ..$ hobbies     : chr [1:2] "Marbles" "Animal fancy"
  ..$ purchases   :List of 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25898
  .. .. ..$ Number  : chr "75145"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "Original Content"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Eclipse Fighter"
  .. .. ..$ Pieces  : int 363
  .. .. ..$ USPrice : num 30
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75145-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Lucas"
  ..$ last_name   : chr "Jimenez-Dominguez"
  ..$ age         : num 18
  ..$ phone_number: chr "712-555-0459"
  ..$ hobbies     : chr [1:3] "Hiking" "Mushroom hunting/Mycology" "Metalworking"
  ..$ purchases   :List of 5
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24691
  .. .. ..$ Number  : chr "31043"
  .. .. ..$ Theme   : chr "Creator"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Chopper Transporter"
  .. .. ..$ Pieces  : int 124
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/31043-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 26034
  .. .. ..$ Number  : chr "41573"
  .. .. ..$ Theme   : chr "Mixels"
  .. .. ..$ Subtheme: chr "Series 9"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Sweepz"
  .. .. ..$ Pieces  : int 61
  .. .. ..$ USPrice : num 4.99
  .. .. ..$ ImageURL: chr ""
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24704
  .. .. ..$ Number  : chr "41140"
  .. .. ..$ Theme   : chr "Disney Princess"
  .. .. ..$ Subtheme: chr "Palace Pets"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Daisy's Beauty Salon"
  .. .. ..$ Pieces  : int 98
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41140-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24903
  .. .. ..$ Number  : chr "41558"
  .. .. ..$ Theme   : chr "Mixels"
  .. .. ..$ Subtheme: chr "Series 7"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Mixadel"
  .. .. ..$ Pieces  : int 63
  .. .. ..$ USPrice : num 4.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41558-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 26033
  .. .. ..$ Number  : chr "41572"
  .. .. ..$ Theme   : chr "Mixels"
  .. .. ..$ Subtheme: chr "Series 9"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Gobbol"
  .. .. ..$ Pieces  : int 62
  .. .. ..$ USPrice : num 4.99
  .. .. ..$ ImageURL: chr ""
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Jake"
  ..$ last_name   : chr "Montes Alvarez"
  ..$ age         : num 30
  ..$ phone_number: chr "603-555-6881"
  ..$ hobbies     : chr [1:2] "Fishing" "Mahjong"
  ..$ purchases   :List of 4
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25005
  .. .. ..$ Number  : chr "41566"
  .. .. ..$ Theme   : chr "Mixels"
  .. .. ..$ Subtheme: chr "Series 8"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Sharx"
  .. .. ..$ Pieces  : int 55
  .. .. ..$ USPrice : num 4.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41566-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24751
  .. .. ..$ Number  : chr "76066"
  .. .. ..$ Theme   : chr "Marvel Super Heroes"
  .. .. ..$ Subtheme: chr "Mighty Micros"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Hulk vs. Ultron"
  .. .. ..$ Pieces  : int 80
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/76066-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24704
  .. .. ..$ Number  : chr "41140"
  .. .. ..$ Theme   : chr "Disney Princess"
  .. .. ..$ Subtheme: chr "Palace Pets"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Daisy's Beauty Salon"
  .. .. ..$ Pieces  : int 98
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41140-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25901
  .. .. ..$ Number  : chr "5004612"
  .. .. ..$ Theme   : chr "Gear"
  .. .. ..$ Subtheme: chr "Watches/Clocks"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Lucy Wyldstyle Minifigure Link Watch"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 25
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/5004612-1.jpg"
  .. .. ..$ Quantity: num 3
 $ :List of 6
  ..$ gender    : chr "Male"
  ..$ first_name: chr "Trevon"
  ..$ last_name : chr "Thanh"
  ..$ age       : num 25
  ..$ hobbies   : chr "Ice hockey"
  ..$ purchases :List of 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25612
  .. .. ..$ Number  : chr "21128"
  .. .. ..$ Theme   : chr "Minecraft"
  .. .. ..$ Subtheme: chr "Minifig-scale"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "The Village"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 200
  .. .. ..$ ImageURL: chr ""
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "John'Dunae"
  ..$ last_name   : chr "Higgins"
  ..$ age         : num 19
  ..$ phone_number: chr "813-555-5561"
  ..$ hobbies     : chr [1:2] "Golfing" "Sand art"
  ..$ purchases   :List of 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24744
  .. .. ..$ Number  : chr "76046"
  .. .. ..$ Theme   : chr "DC Comics Super Heroes"
  .. .. ..$ Subtheme: chr "Batman v Superman: Dawn of Justice"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Heroes of Justice: Sky High Battle"
  .. .. ..$ Pieces  : int 517
  .. .. ..$ USPrice : num 60
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/76046-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 6
  ..$ gender    : chr "Male"
  ..$ first_name: chr "Tysen"
  ..$ last_name : chr "Banda-Chavez"
  ..$ age       : num 43
  ..$ hobbies   : chr "Hunting"
  ..$ purchases :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 26059
  .. .. ..$ Number  : chr "5005060"
  .. .. ..$ Theme   : chr "Gear"
  .. .. ..$ Subtheme: chr "Video Games/3DS"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Marvel Avengers Nintendo 3DS Video Game"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 30
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/5005060-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25003
  .. .. ..$ Number  : chr "41564"
  .. .. ..$ Theme   : chr "Mixels"
  .. .. ..$ Subtheme: chr "Series 8"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Aquad"
  .. .. ..$ Pieces  : int 70
  .. .. ..$ USPrice : num 4.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41564-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24677
  .. .. ..$ Number  : chr "60108"
  .. .. ..$ Theme   : chr "City"
  .. .. ..$ Subtheme: chr "Fire"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Fire Response Unit"
  .. .. ..$ Pieces  : int 257
  .. .. ..$ USPrice : num 40
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/60108-1.jpg"
  .. .. ..$ Quantity: num 2
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Janay"
  ..$ last_name   : chr "Gienapp"
  ..$ age         : num 63
  ..$ phone_number: chr "774-555-2102"
  ..$ hobbies     : chr "Paintball"
  ..$ purchases   :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25612
  .. .. ..$ Number  : chr "21128"
  .. .. ..$ Theme   : chr "Minecraft"
  .. .. ..$ Subtheme: chr "Minifig-scale"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "The Village"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 200
  .. .. ..$ ImageURL: chr ""
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24704
  .. .. ..$ Number  : chr "41140"
  .. .. ..$ Theme   : chr "Disney Princess"
  .. .. ..$ Subtheme: chr "Palace Pets"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Daisy's Beauty Salon"
  .. .. ..$ Pieces  : int 98
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41140-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25893
  .. .. ..$ Number  : chr "30349"
  .. .. ..$ Theme   : chr "City"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Sports Car"
  .. .. ..$ Pieces  : int 47
  .. .. ..$ USPrice : num 3.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/30349-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Eric"
  ..$ last_name   : chr "Benally"
  ..$ age         : num 20
  ..$ phone_number: chr "418-555-3696"
  ..$ hobbies     : chr "Archery"
  ..$ purchases   :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24761
  .. .. ..$ Number  : chr "70316"
  .. .. ..$ Theme   : chr "Nexo Knights"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Jestro's Evil Mobile"
  .. .. ..$ Pieces  : int 658
  .. .. ..$ USPrice : num 60
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70316-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25634
  .. .. ..$ Number  : chr "70319"
  .. .. ..$ Theme   : chr "Nexo Knights"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Macy's Thunder Mace"
  .. .. ..$ Pieces  : int 202
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70319-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24900
  .. .. ..$ Number  : chr "41122"
  .. .. ..$ Theme   : chr "Friends"
  .. .. ..$ Subtheme: chr "Adventure Camp"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Adventure Camp Tree House"
  .. .. ..$ Pieces  : int 726
  .. .. ..$ USPrice : num 80
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41122-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 6
  ..$ gender    : chr "Male"
  ..$ first_name: chr "Carson"
  ..$ last_name : chr "Aragon"
  ..$ age       : num 38
  ..$ hobbies   : chr [1:2] "Letterboxing" "Judo"
  ..$ purchases :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25634
  .. .. ..$ Number  : chr "70319"
  .. .. ..$ Theme   : chr "Nexo Knights"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Macy's Thunder Mace"
  .. .. ..$ Pieces  : int 202
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70319-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25910
  .. .. ..$ Number  : chr "30347"
  .. .. ..$ Theme   : chr "City"
  .. .. ..$ Subtheme: chr "Fire"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Fire Car"
  .. .. ..$ Pieces  : int 53
  .. .. ..$ USPrice : num 3.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/30347-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Samantha"
  ..$ last_name   : chr "Haberland"
  ..$ age         : num 21
  ..$ phone_number: chr "705-555-1457"
  ..$ hobbies     : chr "Gunsmithing"
  ..$ purchases   :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25668
  .. .. ..$ Number  : chr "75828"
  .. .. ..$ Theme   : chr "Ghostbusters"
  .. .. ..$ Subtheme: chr "Reboot"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Ghostbusters Ecto-1 & Ecto-2"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 60
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75828-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25644
  .. .. ..$ Number  : chr "71313"
  .. .. ..$ Theme   : chr "Bionicle"
  .. .. ..$ Subtheme: chr "Reboot Villains"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Lava Beast"
  .. .. ..$ Pieces  : int 114
  .. .. ..$ USPrice : num 15
  .. .. ..$ ImageURL: chr ""
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24764
  .. .. ..$ Number  : chr "70333"
  .. .. ..$ Theme   : chr "Nexo Knights"
  .. .. ..$ Subtheme: chr "Ultimate"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Ultimate Robin"
  .. .. ..$ Pieces  : int 75
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70333-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Cameron"
  ..$ last_name   : chr "Rodriguez"
  ..$ age         : num 48
  ..$ phone_number: chr "325-555-1926"
  ..$ hobbies     : chr [1:2] "Table tennis" "Kayaking"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25879
  .. .. ..$ Number  : chr "853534"
  .. .. ..$ Theme   : chr "Gear"
  .. .. ..$ Subtheme: chr "Key Chains/Ninjago"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Airjitzu Jay Key Chain"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 5.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/853534-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25910
  .. .. ..$ Number  : chr "30347"
  .. .. ..$ Theme   : chr "City"
  .. .. ..$ Subtheme: chr "Fire"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Fire Car"
  .. .. ..$ Pieces  : int 53
  .. .. ..$ USPrice : num 3.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/30347-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Connor"
  ..$ last_name   : chr "Padilla"
  ..$ age         : num 36
  ..$ phone_number: chr "441-555-6534"
  ..$ hobbies     : chr [1:3] "Coin collecting" "Knife making" "Video game collecting"
  ..$ purchases   :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24674
  .. .. ..$ Number  : chr "71310"
  .. .. ..$ Theme   : chr "Bionicle"
  .. .. ..$ Subtheme: chr "Reboot Villains"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Umarak the Hunter"
  .. .. ..$ Pieces  : int 172
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/71310-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24902
  .. .. ..$ Number  : chr "41556"
  .. .. ..$ Theme   : chr "Mixels"
  .. .. ..$ Subtheme: chr "Series 7"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Tiketz"
  .. .. ..$ Pieces  : int 62
  .. .. ..$ USPrice : num 4.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41556-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24797
  .. .. ..$ Number  : chr "75138"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "Episode V"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Hoth Attack"
  .. .. ..$ Pieces  : int 233
  .. .. ..$ USPrice : num 25
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75138-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Tyrii"
  ..$ last_name   : chr "Bloom"
  ..$ age         : num 23
  ..$ phone_number: chr "784-555-7128"
  ..$ hobbies     : chr [1:2] "Rugby" "Astrology"
  ..$ purchases   :List of 4
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24759
  .. .. ..$ Number  : chr "70313"
  .. .. ..$ Theme   : chr "Nexo Knights"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Moltor's Lava Smasher"
  .. .. ..$ Pieces  : int 187
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70313-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24735
  .. .. ..$ Number  : chr "41120"
  .. .. ..$ Theme   : chr "Friends"
  .. .. ..$ Subtheme: chr "Adventure Camp"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Adventure Camp Archery"
  .. .. ..$ Pieces  : int 114
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41120-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24692
  .. .. ..$ Number  : chr "31044"
  .. .. ..$ Theme   : chr "Creator"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Park Animals"
  .. .. ..$ Pieces  : int 202
  .. .. ..$ USPrice : num 15
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/31044-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24737
  .. .. ..$ Number  : chr "41135"
  .. .. ..$ Theme   : chr "Friends"
  .. .. ..$ Subtheme: chr "Pop Star"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Livi's Pop Star House"
  .. .. ..$ Pieces  : int 597
  .. .. ..$ USPrice : num 50
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41135-1.jpg"
  .. .. ..$ Quantity: num 3
 $ :List of 6
  ..$ gender    : chr "Male"
  ..$ first_name: chr "Austin"
  ..$ last_name : chr "Martinez"
  ..$ age       : num 29
  ..$ hobbies   : chr [1:2] "Electronics" "Seashell collecting"
  ..$ purchases :List of 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24769
  .. .. ..$ Number  : chr "70600"
  .. .. ..$ Theme   : chr "Ninjago"
  .. .. ..$ Subtheme: chr "Skybound"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Ninja Bike Chase"
  .. .. ..$ Pieces  : int 231
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70600-1.jpg"
  .. .. ..$ Quantity: num 2
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Caroline"
  ..$ last_name   : chr "Holstein"
  ..$ age         : num 38
  ..$ phone_number: chr "318-555-7894"
  ..$ hobbies     : chr [1:2] "Darts" "Knitting"
  ..$ purchases   :List of 5
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24798
  .. .. ..$ Number  : chr "75140"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "The Force Awakens"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Resistance Troop Transporter"
  .. .. ..$ Pieces  : int 646
  .. .. ..$ USPrice : num 70
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75140-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24763
  .. .. ..$ Number  : chr "70331"
  .. .. ..$ Theme   : chr "Nexo Knights"
  .. .. ..$ Subtheme: chr "Ultimate"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Ultimate Macy"
  .. .. ..$ Pieces  : int 101
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70331-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24678
  .. .. ..$ Number  : chr "60109"
  .. .. ..$ Theme   : chr "City"
  .. .. ..$ Subtheme: chr "Fire"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Fire Boat"
  .. .. ..$ Pieces  : int 412
  .. .. ..$ USPrice : num 80
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/60109-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24959
  .. .. ..$ Number  : chr "75139"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "The Force Awakens"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Battle on Takodana"
  .. .. ..$ Pieces  : int 409
  .. .. ..$ USPrice : num 60
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75139-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24699
  .. .. ..$ Number  : chr "76053"
  .. .. ..$ Theme   : chr "DC Comics Super Heroes"
  .. .. ..$ Subtheme: chr "Batman"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Gotham City Cycle Chase"
  .. .. ..$ Pieces  : int 224
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/76053-1.jpg"
  .. .. ..$ Quantity: num 3
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Joshua"
  ..$ last_name   : chr "Long"
  ..$ age         : num 55
  ..$ phone_number: chr "469-555-6245"
  ..$ hobbies     : chr [1:2] "Animal fancy" "Cryptography"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 26056
  .. .. ..$ Number  : chr "5005057"
  .. .. ..$ Theme   : chr "Gear"
  .. .. ..$ Subtheme: chr "Video Games/XBOX 360"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Marvel Avengers XBOX 360 Video Game"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 50
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/5005057-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 26057
  .. .. ..$ Number  : chr "5005058"
  .. .. ..$ Theme   : chr "Gear"
  .. .. ..$ Subtheme: chr "Video Games/Wii U"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Marvel Avengers Wii U Video Game"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 50
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/5005058-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 6
  ..$ gender    : chr "Male"
  ..$ first_name: chr "Binh"
  ..$ last_name : chr "Skalla"
  ..$ age       : num 23
  ..$ hobbies   : chr "Auto audiophilia"
  ..$ purchases :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24685
  .. .. ..$ Number  : chr "60118"
  .. .. ..$ Theme   : chr "City"
  .. .. ..$ Subtheme: chr "Traffic"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Garbage Truck"
  .. .. ..$ Pieces  : int 248
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/60118-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24781
  .. .. ..$ Number  : chr "75116"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "Buildable Figures"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Finn"
  .. .. ..$ Pieces  : int 98
  .. .. ..$ USPrice : num 25
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75116-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24736
  .. .. ..$ Number  : chr "41121"
  .. .. ..$ Theme   : chr "Friends"
  .. .. ..$ Subtheme: chr "Adventure Camp"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Adventure Camp Rafting"
  .. .. ..$ Pieces  : int 320
  .. .. ..$ USPrice : num 30
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41121-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Nicholas"
  ..$ last_name   : chr "Scott"
  ..$ age         : num 57
  ..$ phone_number: chr "418-555-1075"
  ..$ hobbies     : chr "Climbing"
  ..$ purchases   :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24758
  .. .. ..$ Number  : chr "70312"
  .. .. ..$ Theme   : chr "Nexo Knights"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Lance's Mecha Horse"
  .. .. ..$ Pieces  : int 237
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70312-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25881
  .. .. ..$ Number  : chr "853549"
  .. .. ..$ Theme   : chr "Gear"
  .. .. ..$ Subtheme: chr "Key Chains/Friends"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Mia Key Chain"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 5.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/853549-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25885
  .. .. ..$ Number  : chr "853572"
  .. .. ..$ Theme   : chr "Gear"
  .. .. ..$ Subtheme: chr "Key Chains/Miscellaneous"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Bumble Bee Key Chain"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 5.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/853572-1.jpg"
  .. .. ..$ Quantity: num 2
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Jacob"
  ..$ last_name   : chr "Barron"
  ..$ age         : num 27
  ..$ phone_number: chr "319-555-6104"
  ..$ hobbies     : chr "Animal fancy"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24680
  .. .. ..$ Number  : chr "60113"
  .. .. ..$ Theme   : chr "City"
  .. .. ..$ Subtheme: chr "Traffic"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Rally Car"
  .. .. ..$ Pieces  : int 104
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/60113-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24792
  .. .. ..$ Number  : chr "75134"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "Battlefront"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Galactic Empire Battle Pack"
  .. .. ..$ Pieces  : int 109
  .. .. ..$ USPrice : num 13
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75134-1.jpg"
  .. .. ..$ Quantity: num 2
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Madeline"
  ..$ last_name   : chr "Castor"
  ..$ age         : num 39
  ..$ phone_number: chr "450-555-9877"
  ..$ hobbies     : chr [1:2] "Kitesurfing" "Baseball"
  ..$ purchases   :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25006
  .. .. ..$ Number  : chr "41567"
  .. .. ..$ Theme   : chr "Mixels"
  .. .. ..$ Subtheme: chr "Series 8"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Skulzy"
  .. .. ..$ Pieces  : int 66
  .. .. ..$ USPrice : num 4.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41567-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25969
  .. .. ..$ Number  : chr "76059"
  .. .. ..$ Theme   : chr "Marvel Super Heroes"
  .. .. ..$ Subtheme: chr "Ultimate Spider-Man"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Spider-Man: Doc Ock's Tentacle Trap"
  .. .. ..$ Pieces  : int 446
  .. .. ..$ USPrice : num 40
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/76059-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 26025
  .. .. ..$ Number  : chr "41178"
  .. .. ..$ Theme   : chr "Elves"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "The Dragon Sanctuary"
  .. .. ..$ Pieces  : int 585
  .. .. ..$ USPrice : num 50
  .. .. ..$ ImageURL: chr ""
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Trevor"
  ..$ last_name   : chr "Perez"
  ..$ age         : num 39
  ..$ phone_number: chr "878-555-5155"
  ..$ hobbies     : chr "Deltiology (postcard collecting)"
  ..$ purchases   :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24730
  .. .. ..$ Number  : chr "41115"
  .. .. ..$ Theme   : chr "Friends"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Emma's Creative Workshop"
  .. .. ..$ Pieces  : int 108
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41115-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24746
  .. .. ..$ Number  : chr "76048"
  .. .. ..$ Theme   : chr "Marvel Super Heroes"
  .. .. ..$ Subtheme: chr "Avengers Assemble"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Iron Skull Sub Attack"
  .. .. ..$ Pieces  : int 335
  .. .. ..$ USPrice : num 30
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/76048-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24703
  .. .. ..$ Number  : chr "41069"
  .. .. ..$ Theme   : chr "Disney Princess"
  .. .. ..$ Subtheme: chr "Palace Pets"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Treasure's Day at the Pool"
  .. .. ..$ Pieces  : int 70
  .. .. ..$ USPrice : num 5.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41069-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "David"
  ..$ last_name   : chr "Cabral"
  ..$ age         : num 19
  ..$ phone_number: chr "415-555-8642"
  ..$ hobbies     : chr "Insect collecting"
  ..$ purchases   :List of 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24957
  .. .. ..$ Number  : chr "71309"
  .. .. ..$ Theme   : chr "Bionicle"
  .. .. ..$ Subtheme: chr "Toa"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Onua - Uniter of Earth"
  .. .. ..$ Pieces  : int 143
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/71309-1.jpg"
  .. .. ..$ Quantity: num 2
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Adam"
  ..$ last_name   : chr "Albornoz"
  ..$ age         : num 36
  ..$ phone_number: chr "418-555-2486"
  ..$ hobbies     : chr [1:2] "Sewing" "Hunting"
  ..$ purchases   :List of 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24907
  .. .. ..$ Number  : chr "42050"
  .. .. ..$ Theme   : chr "Technic"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Drag Racer"
  .. .. ..$ Pieces  : int 647
  .. .. ..$ USPrice : num 80
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/42050-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Manuel"
  ..$ last_name   : chr "Wilkerson"
  ..$ age         : num 23
  ..$ phone_number: chr "441-555-3652"
  ..$ hobbies     : chr [1:3] "Radio-controlled car racing" "Handball" "Sculling or Rowing"
  ..$ purchases   :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24725
  .. .. ..$ Number  : chr "41174"
  .. .. ..$ Theme   : chr "Elves"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "The Starlight Inn"
  .. .. ..$ Pieces  : int 343
  .. .. ..$ USPrice : num 30
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41174-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24751
  .. .. ..$ Number  : chr "76066"
  .. .. ..$ Theme   : chr "Marvel Super Heroes"
  .. .. ..$ Subtheme: chr "Mighty Micros"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Hulk vs. Ultron"
  .. .. ..$ Pieces  : int 80
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/76066-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24768
  .. .. ..$ Number  : chr "70599"
  .. .. ..$ Theme   : chr "Ninjago"
  .. .. ..$ Subtheme: chr "Skybound"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Cole's Dragon"
  .. .. ..$ Pieces  : int 98
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70599-1.jpg"
  .. .. ..$ Quantity: num 2
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Dakota"
  ..$ last_name   : chr "Klopp"
  ..$ age         : num 33
  ..$ phone_number: chr "970-555-9320"
  ..$ hobbies     : chr [1:2] "Art collecting" "Cycling"
  ..$ purchases   :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25660
  .. .. ..$ Number  : chr "75822"
  .. .. ..$ Theme   : chr "The Angry Birds Movie"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Piggy Plane Attack"
  .. .. ..$ Pieces  : int 168
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75822-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24807
  .. .. ..$ Number  : chr "71235"
  .. .. ..$ Theme   : chr "Dimensions"
  .. .. ..$ Subtheme: chr "Level Pack"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Level Pack: Midway Arcade"
  .. .. ..$ Pieces  : int 96
  .. .. ..$ USPrice : num 30
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/71235-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25006
  .. .. ..$ Number  : chr "41567"
  .. .. ..$ Theme   : chr "Mixels"
  .. .. ..$ Subtheme: chr "Series 8"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Skulzy"
  .. .. ..$ Pieces  : int 66
  .. .. ..$ USPrice : num 4.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41567-1.jpg"
  .. .. ..$ Quantity: num 2
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Aleksandr"
  ..$ last_name   : chr "Gurrola"
  ..$ age         : num 61
  ..$ phone_number: chr "508-555-9403"
  ..$ hobbies     : chr(0) 
  ..$ purchases   :List of 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25910
  .. .. ..$ Number  : chr "30347"
  .. .. ..$ Theme   : chr "City"
  .. .. ..$ Subtheme: chr "Fire"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Fire Car"
  .. .. ..$ Pieces  : int 53
  .. .. ..$ USPrice : num 3.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/30347-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 6
  ..$ gender    : chr "Male"
  ..$ first_name: chr "Michael"
  ..$ last_name : chr "Hernandez Muniz"
  ..$ age       : num 62
  ..$ hobbies   : chr [1:2] "Jewelry making" "Kitesurfing"
  ..$ purchases :List of 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24745
  .. .. ..$ Number  : chr "76047"
  .. .. ..$ Theme   : chr "Marvel Super Heroes"
  .. .. ..$ Subtheme: chr "Captain America: Civil War"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Black Panther Pursuit"
  .. .. ..$ Pieces  : int 287
  .. .. ..$ USPrice : num 30
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/76047-1.jpg"
  .. .. ..$ Quantity: num 2
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Xavier"
  ..$ last_name   : chr "Suazo"
  ..$ age         : num 27
  ..$ phone_number: chr "321-555-0605"
  ..$ hobbies     : chr [1:2] "Mineral collecting" "Creative writing"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24779
  .. .. ..$ Number  : chr "75114"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "Buildable Figures"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "First Order Stormtrooper"
  .. .. ..$ Pieces  : int 81
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75114-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24771
  .. .. ..$ Number  : chr "70603"
  .. .. ..$ Theme   : chr "Ninjago"
  .. .. ..$ Subtheme: chr "Skybound"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Raid Zeppelin"
  .. .. ..$ Pieces  : int 294
  .. .. ..$ USPrice : num 30
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70603-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Jaime"
  ..$ last_name   : chr "Rideout"
  ..$ age         : num 26
  ..$ phone_number: chr "913-555-5139"
  ..$ hobbies     : chr [1:2] "Vacation" "Cricket"
  ..$ purchases   :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25641
  .. .. ..$ Number  : chr "70326"
  .. .. ..$ Theme   : chr "Nexo Knights"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "The Black Knight Mech"
  .. .. ..$ Pieces  : int 530
  .. .. ..$ USPrice : num 40
  .. .. ..$ ImageURL: chr ""
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24717
  .. .. ..$ Number  : chr "10818"
  .. .. ..$ Theme   : chr "Duplo"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "My First Truck"
  .. .. ..$ Pieces  : int 29
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/10818-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24899
  .. .. ..$ Number  : chr "41114"
  .. .. ..$ Theme   : chr "Friends"
  .. .. ..$ Subtheme: chr "Party"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Party Styling"
  .. .. ..$ Pieces  : int 54
  .. .. ..$ USPrice : num 4.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41114-1.jpg"
  .. .. ..$ Quantity: num 2
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Tj"
  ..$ last_name   : chr "Aguon"
  ..$ age         : num 47
  ..$ phone_number: chr "862-555-5629"
  ..$ hobbies     : chr "Graffiti"
  ..$ purchases   :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24737
  .. .. ..$ Number  : chr "41135"
  .. .. ..$ Theme   : chr "Friends"
  .. .. ..$ Subtheme: chr "Pop Star"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Livi's Pop Star House"
  .. .. ..$ Pieces  : int 597
  .. .. ..$ USPrice : num 50
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41135-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24894
  .. .. ..$ Number  : chr "31040"
  .. .. ..$ Theme   : chr "Creator"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Desert Racers"
  .. .. ..$ Pieces  : int 65
  .. .. ..$ USPrice : num 4.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/31040-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24720
  .. .. ..$ Number  : chr "10830"
  .. .. ..$ Theme   : chr "Duplo"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Minnie's Café"
  .. .. ..$ Pieces  : int 27
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/10830-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Taylor"
  ..$ last_name   : chr "Allen"
  ..$ age         : num 41
  ..$ phone_number: chr "760-555-8123"
  ..$ hobbies     : chr [1:2] "Fashion" "Ice skating"
  ..$ purchases   :List of 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25923
  .. .. ..$ Number  : chr "75147"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "Original Content"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Star Scavenger"
  .. .. ..$ Pieces  : int 558
  .. .. ..$ USPrice : num 50
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75147-1.jpg"
  .. .. ..$ Quantity: num 2
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Kaitlyn"
  ..$ last_name   : chr "Degeer"
  ..$ age         : num 24
  ..$ phone_number: chr "316-555-7890"
  ..$ hobbies     : chr [1:3] "Wood carving" "Fencing" "Fishing"
  ..$ purchases   :List of 4
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25887
  .. .. ..$ Number  : chr "853543"
  .. .. ..$ Theme   : chr "Ninjago"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Ninjago Party Set"
  .. .. ..$ Pieces  : int 70
  .. .. ..$ USPrice : num 7.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/853543-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24765
  .. .. ..$ Number  : chr "70332"
  .. .. ..$ Theme   : chr "Nexo Knights"
  .. .. ..$ Subtheme: chr "Ultimate"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Ultimate Aaron"
  .. .. ..$ Pieces  : int 82
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70332-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 26035
  .. .. ..$ Number  : chr "41574"
  .. .. ..$ Theme   : chr "Mixels"
  .. .. ..$ Subtheme: chr "Series 9"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Compax"
  .. .. ..$ Pieces  : int 66
  .. .. ..$ USPrice : num 4.99
  .. .. ..$ ImageURL: chr ""
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24994
  .. .. ..$ Number  : chr "10251"
  .. .. ..$ Theme   : chr "Advanced Models"
  .. .. ..$ Subtheme: chr "Modular Buildings"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Brick Bank"
  .. .. ..$ Pieces  : int 2380
  .. .. ..$ USPrice : num 170
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/10251-1.jpg"
  .. .. ..$ Quantity: num 2
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Matthew"
  ..$ last_name   : chr "Sandoval"
  ..$ age         : num 22
  ..$ phone_number: chr "671-555-7044"
  ..$ hobbies     : chr [1:3] "Knife throwing" "Skateboarding" "Amateur radio"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25660
  .. .. ..$ Number  : chr "75822"
  .. .. ..$ Theme   : chr "The Angry Birds Movie"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Piggy Plane Attack"
  .. .. ..$ Pieces  : int 168
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75822-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25884
  .. .. ..$ Number  : chr "853571"
  .. .. ..$ Theme   : chr "Gear"
  .. .. ..$ Subtheme: chr "Key Chains/Miscellaneous"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Hot Dog Guy Key Chain"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 5.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/853571-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Jordan"
  ..$ last_name   : chr "West"
  ..$ age         : num 56
  ..$ phone_number: chr "810-555-1608"
  ..$ hobbies     : chr [1:2] "Shooting sport" "Table tennis"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24898
  .. .. ..$ Number  : chr "41113"
  .. .. ..$ Theme   : chr "Friends"
  .. .. ..$ Subtheme: chr "Party"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Party Gift Shop"
  .. .. ..$ Pieces  : int 52
  .. .. ..$ USPrice : num 4.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41113-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24711
  .. .. ..$ Number  : chr "10807"
  .. .. ..$ Theme   : chr "Duplo"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Horse Trailer"
  .. .. ..$ Pieces  : int 15
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/10807-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Reyes"
  ..$ last_name   : chr "Wilson"
  ..$ age         : num 33
  ..$ phone_number: chr "605-555-2774"
  ..$ hobbies     : chr "Seashell collecting"
  ..$ purchases   :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24903
  .. .. ..$ Number  : chr "41558"
  .. .. ..$ Theme   : chr "Mixels"
  .. .. ..$ Subtheme: chr "Series 7"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Mixadel"
  .. .. ..$ Pieces  : int 63
  .. .. ..$ USPrice : num 4.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41558-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24693
  .. .. ..$ Number  : chr "31045"
  .. .. ..$ Theme   : chr "Creator"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Ocean Explorer"
  .. .. ..$ Pieces  : int 213
  .. .. ..$ USPrice : num 15
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/31045-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24793
  .. .. ..$ Number  : chr "75133"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "Battlefront"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Rebel Alliance Battle Pack"
  .. .. ..$ Pieces  : int 101
  .. .. ..$ USPrice : num 13
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75133-1.jpg"
  .. .. ..$ Quantity: num 2
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Avery"
  ..$ last_name   : chr "Leung"
  ..$ age         : num 33
  ..$ phone_number: chr "330-555-2699"
  ..$ hobbies     : chr [1:2] "Scuba diving" "Sketching"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24781
  .. .. ..$ Number  : chr "75116"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "Buildable Figures"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Finn"
  .. .. ..$ Pieces  : int 98
  .. .. ..$ USPrice : num 25
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75116-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25876
  .. .. ..$ Number  : chr "853555"
  .. .. ..$ Theme   : chr "Gear"
  .. .. ..$ Subtheme: chr "Stationery"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Campsite Scrapbook"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 15
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/853555-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Michael"
  ..$ last_name   : chr "Williams"
  ..$ age         : num 31
  ..$ phone_number: chr "936-555-2974"
  ..$ hobbies     : chr(0) 
  ..$ purchases   :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24988
  .. .. ..$ Number  : chr "40202"
  .. .. ..$ Theme   : chr "Seasonal"
  .. .. ..$ Subtheme: chr "Easter"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Easter Chick"
  .. .. ..$ Pieces  : int 111
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr ""
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24672
  .. .. ..$ Number  : chr "71307"
  .. .. ..$ Theme   : chr "Bionicle"
  .. .. ..$ Subtheme: chr "Toa"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Gali - Uniter of Water"
  .. .. ..$ Pieces  : int 87
  .. .. ..$ USPrice : num 15
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/71307-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24895
  .. .. ..$ Number  : chr "31041"
  .. .. ..$ Theme   : chr "Creator"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Construction Vehicles"
  .. .. ..$ Pieces  : int 64
  .. .. ..$ USPrice : num 4.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/31041-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Colleen"
  ..$ last_name   : chr "Galley"
  ..$ age         : num 31
  ..$ phone_number: chr "710-555-8843"
  ..$ hobbies     : chr "Field hockey"
  ..$ purchases   :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24705
  .. .. ..$ Number  : chr "41141"
  .. .. ..$ Theme   : chr "Disney Princess"
  .. .. ..$ Subtheme: chr "Palace Pets"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Pumpkin's Royal Carriage"
  .. .. ..$ Pieces  : int 79
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41141-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24976
  .. .. ..$ Number  : chr "60105"
  .. .. ..$ Theme   : chr "City"
  .. .. ..$ Subtheme: chr "Fire"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Fire ATV"
  .. .. ..$ Pieces  : int 64
  .. .. ..$ USPrice : num 6.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/60105-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24956
  .. .. ..$ Number  : chr "71300"
  .. .. ..$ Theme   : chr "Bionicle"
  .. .. ..$ Subtheme: chr "companions"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Uxar - Creature of Jungle"
  .. .. ..$ Pieces  : int 89
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/71300-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Brandilyn"
  ..$ last_name   : chr "Robertson"
  ..$ age         : num 27
  ..$ phone_number: chr "724-555-5496"
  ..$ hobbies     : chr(0) 
  ..$ purchases   :List of 5
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24703
  .. .. ..$ Number  : chr "41069"
  .. .. ..$ Theme   : chr "Disney Princess"
  .. .. ..$ Subtheme: chr "Palace Pets"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Treasure's Day at the Pool"
  .. .. ..$ Pieces  : int 70
  .. .. ..$ USPrice : num 5.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41069-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25886
  .. .. ..$ Number  : chr "853519"
  .. .. ..$ Theme   : chr "Gear"
  .. .. ..$ Subtheme: chr "Playmats"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "NK Playmat"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 15
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/853519-1.jpg"
  .. .. ..$ Quantity: num 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24704
  .. .. ..$ Number  : chr "41140"
  .. .. ..$ Theme   : chr "Disney Princess"
  .. .. ..$ Subtheme: chr "Palace Pets"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Daisy's Beauty Salon"
  .. .. ..$ Pieces  : int 98
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41140-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25635
  .. .. ..$ Number  : chr "70320"
  .. .. ..$ Theme   : chr "Nexo Knights"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Aaron Fox's Aero-Striker V2"
  .. .. ..$ Pieces  : int 301
  .. .. ..$ USPrice : num 30
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70320-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24745
  .. .. ..$ Number  : chr "76047"
  .. .. ..$ Theme   : chr "Marvel Super Heroes"
  .. .. ..$ Subtheme: chr "Captain America: Civil War"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Black Panther Pursuit"
  .. .. ..$ Pieces  : int 287
  .. .. ..$ USPrice : num 30
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/76047-1.jpg"
  .. .. ..$ Quantity: num 2
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Son"
  ..$ last_name   : chr "Saldanha"
  ..$ age         : num 30
  ..$ phone_number: chr "507-555-2278"
  ..$ hobbies     : chr(0) 
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25878
  .. .. ..$ Number  : chr "853505"
  .. .. ..$ Theme   : chr "Gear"
  .. .. ..$ Subtheme: chr "Role-Play toys"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "NK Sword Standard"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/853505-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24793
  .. .. ..$ Number  : chr "75133"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "Battlefront"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Rebel Alliance Battle Pack"
  .. .. ..$ Pieces  : int 101
  .. .. ..$ USPrice : num 13
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75133-1.jpg"
  .. .. ..$ Quantity: num 2
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Katherine"
  ..$ last_name   : chr "Beck"
  ..$ age         : num 45
  ..$ phone_number: chr "209-555-7105"
  ..$ hobbies     : chr [1:2] "Rugby league football" "Scuba diving"
  ..$ purchases   :List of 4
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24994
  .. .. ..$ Number  : chr "10251"
  .. .. ..$ Theme   : chr "Advanced Models"
  .. .. ..$ Subtheme: chr "Modular Buildings"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Brick Bank"
  .. .. ..$ Pieces  : int 2380
  .. .. ..$ USPrice : num 170
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/10251-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24959
  .. .. ..$ Number  : chr "75139"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "The Force Awakens"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Battle on Takodana"
  .. .. ..$ Pieces  : int 409
  .. .. ..$ USPrice : num 60
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75139-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24758
  .. .. ..$ Number  : chr "70312"
  .. .. ..$ Theme   : chr "Nexo Knights"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Lance's Mecha Horse"
  .. .. ..$ Pieces  : int 237
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70312-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 26025
  .. .. ..$ Number  : chr "41178"
  .. .. ..$ Theme   : chr "Elves"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "The Dragon Sanctuary"
  .. .. ..$ Pieces  : int 585
  .. .. ..$ USPrice : num 50
  .. .. ..$ ImageURL: chr ""
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Beemnet"
  ..$ last_name   : chr "Masters"
  ..$ age         : num 41
  ..$ phone_number: chr "902-555-8429"
  ..$ hobbies     : chr [1:2] "Astrology" "Sculling or Rowing"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24678
  .. .. ..$ Number  : chr "60109"
  .. .. ..$ Theme   : chr "City"
  .. .. ..$ Subtheme: chr "Fire"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Fire Boat"
  .. .. ..$ Pieces  : int 412
  .. .. ..$ USPrice : num 80
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/60109-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24794
  .. .. ..$ Number  : chr "75135"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "Episode III"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Obi-Wan's Jedi Interceptor"
  .. .. ..$ Pieces  : int 215
  .. .. ..$ USPrice : num 25
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75135-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Shylynn"
  ..$ last_name   : chr "Seitz"
  ..$ age         : num 28
  ..$ phone_number: chr "205-555-7084"
  ..$ hobbies     : chr "Kombucha Brewing"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24756
  .. .. ..$ Number  : chr "70310"
  .. .. ..$ Theme   : chr "Nexo Knights"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Knighton Battle Blaster"
  .. .. ..$ Pieces  : int 76
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70310-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24679
  .. .. ..$ Number  : chr "60111"
  .. .. ..$ Theme   : chr "City"
  .. .. ..$ Subtheme: chr "Fire"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Fire Utility Truck"
  .. .. ..$ Pieces  : int 368
  .. .. ..$ USPrice : num 40
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/60111-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Sonny"
  ..$ last_name   : chr "Smith"
  ..$ age         : num 24
  ..$ phone_number: chr "246-555-7913"
  ..$ hobbies     : chr [1:2] "Web surfing" "Kitesurfing"
  ..$ purchases   :List of 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24699
  .. .. ..$ Number  : chr "76053"
  .. .. ..$ Theme   : chr "DC Comics Super Heroes"
  .. .. ..$ Subtheme: chr "Batman"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Gotham City Cycle Chase"
  .. .. ..$ Pieces  : int 224
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/76053-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Joshua"
  ..$ last_name   : chr "Reyes"
  ..$ age         : num 53
  ..$ phone_number: chr "251-555-5985"
  ..$ hobbies     : chr [1:2] "Antiquities" "Urban exploration"
  ..$ purchases   :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25605
  .. .. ..$ Number  : chr "75146"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "Seasonal"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Star Wars Advent Calendar"
  .. .. ..$ Pieces  : int 282
  .. .. ..$ USPrice : num 40
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75146-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24780
  .. .. ..$ Number  : chr "75115"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "Buildable Figures"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Poe Dameron"
  .. .. ..$ Pieces  : int 102
  .. .. ..$ USPrice : num 25
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75115-1.jpg"
  .. .. ..$ Quantity: num 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24618
  .. .. ..$ Number  : chr "71238"
  .. .. ..$ Theme   : chr "Dimensions"
  .. .. ..$ Subtheme: chr "Fun Pack"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Fun Pack: Cyberman"
  .. .. ..$ Pieces  : int 40
  .. .. ..$ USPrice : num 15
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/71238-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Asia"
  ..$ last_name   : chr "Salyer"
  ..$ age         : num 24
  ..$ phone_number: chr "508-555-0418"
  ..$ hobbies     : chr [1:2] "Darts" "Sculling or Rowing"
  ..$ purchases   :List of 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24751
  .. .. ..$ Number  : chr "76066"
  .. .. ..$ Theme   : chr "Marvel Super Heroes"
  .. .. ..$ Subtheme: chr "Mighty Micros"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Hulk vs. Ultron"
  .. .. ..$ Pieces  : int 80
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/76066-1.jpg"
  .. .. ..$ Quantity: num 3
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Neil"
  ..$ last_name   : chr "Gabel"
  ..$ age         : num 30
  ..$ phone_number: chr "508-555-5700"
  ..$ hobbies     : chr [1:2] "Hiking/backpacking" "Poi"
  ..$ purchases   :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 26056
  .. .. ..$ Number  : chr "5005057"
  .. .. ..$ Theme   : chr "Gear"
  .. .. ..$ Subtheme: chr "Video Games/XBOX 360"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Marvel Avengers XBOX 360 Video Game"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 50
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/5005057-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 26058
  .. .. ..$ Number  : chr "5005059"
  .. .. ..$ Theme   : chr "Gear"
  .. .. ..$ Subtheme: chr "Video Games/PS3"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Marvel Avengers PS3 Video Game"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 50
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/5005059-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24672
  .. .. ..$ Number  : chr "71307"
  .. .. ..$ Theme   : chr "Bionicle"
  .. .. ..$ Subtheme: chr "Toa"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Gali - Uniter of Water"
  .. .. ..$ Pieces  : int 87
  .. .. ..$ USPrice : num 15
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/71307-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Chayanne"
  ..$ last_name   : chr "Williams"
  ..$ age         : num 17
  ..$ phone_number: chr "869-555-6681"
  ..$ hobbies     : chr(0) 
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24678
  .. .. ..$ Number  : chr "60109"
  .. .. ..$ Theme   : chr "City"
  .. .. ..$ Subtheme: chr "Fire"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Fire Boat"
  .. .. ..$ Pieces  : int 412
  .. .. ..$ USPrice : num 80
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/60109-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24697
  .. .. ..$ Number  : chr "76044"
  .. .. ..$ Theme   : chr "DC Comics Super Heroes"
  .. .. ..$ Subtheme: chr "Batman v Superman: Dawn of Justice"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Clash of the Heroes"
  .. .. ..$ Pieces  : int 92
  .. .. ..$ USPrice : num 13
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/76044-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Demetri"
  ..$ last_name   : chr "Do"
  ..$ age         : num 21
  ..$ phone_number: chr "541-555-1433"
  ..$ hobbies     : chr "People watching"
  ..$ purchases   :List of 4
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24665
  .. .. ..$ Number  : chr "21031"
  .. .. ..$ Theme   : chr "Architecture"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Burj Khalifa"
  .. .. ..$ Pieces  : int 333
  .. .. ..$ USPrice : num 40
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/21031-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25620
  .. .. ..$ Number  : chr "70588"
  .. .. ..$ Theme   : chr "Ninjago"
  .. .. ..$ Subtheme: chr "Rise of the Villains"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Titanium Ninja Tumbler "
  .. .. ..$ Pieces  : int 342
  .. .. ..$ USPrice : num 30
  .. .. ..$ ImageURL: chr ""
  .. .. ..$ Quantity: num 4
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24917
  .. .. ..$ Number  : chr "70314"
  .. .. ..$ Theme   : chr "Nexo Knights"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Beast Master's Chaos Chariot"
  .. .. ..$ Pieces  : int 314
  .. .. ..$ USPrice : num 30
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70314-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24794
  .. .. ..$ Number  : chr "75135"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "Episode III"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Obi-Wan's Jedi Interceptor"
  .. .. ..$ Pieces  : int 215
  .. .. ..$ USPrice : num 25
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75135-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Brittany"
  ..$ last_name   : chr "Mclellan"
  ..$ age         : num 25
  ..$ phone_number: chr "210-555-0265"
  ..$ hobbies     : chr "Judo"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24662
  .. .. ..$ Number  : chr "21026"
  .. .. ..$ Theme   : chr "Architecture"
  .. .. ..$ Subtheme: chr "Skylines"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Venice"
  .. .. ..$ Pieces  : int 212
  .. .. ..$ USPrice : num 30
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/21026-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24717
  .. .. ..$ Number  : chr "10818"
  .. .. ..$ Theme   : chr "Duplo"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "My First Truck"
  .. .. ..$ Pieces  : int 29
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/10818-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Joseph"
  ..$ last_name   : chr "Ross"
  ..$ age         : num 33
  ..$ phone_number: chr "254-555-7628"
  ..$ hobbies     : chr [1:2] "Inline skating" "Herping"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24794
  .. .. ..$ Number  : chr "75135"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "Episode III"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Obi-Wan's Jedi Interceptor"
  .. .. ..$ Pieces  : int 215
  .. .. ..$ USPrice : num 25
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75135-1.jpg"
  .. .. ..$ Quantity: num 4
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24684
  .. .. ..$ Number  : chr "60117"
  .. .. ..$ Theme   : chr "City"
  .. .. ..$ Subtheme: chr "Traffic"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Van & Caravan"
  .. .. ..$ Pieces  : int 250
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/60117-1.jpg"
  .. .. ..$ Quantity: num 2
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Paige"
  ..$ last_name   : chr "Wagner"
  ..$ age         : num 35
  ..$ phone_number: chr "860-555-1618"
  ..$ hobbies     : chr [1:2] "Snowboarding" "Aqua-lung"
  ..$ purchases   :List of 4
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 26038
  .. .. ..$ Number  : chr "41577"
  .. .. ..$ Theme   : chr "Mixels"
  .. .. ..$ Subtheme: chr "Series 9"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Mysto"
  .. .. ..$ Pieces  : int 64
  .. .. ..$ USPrice : num 4.99
  .. .. ..$ ImageURL: chr ""
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24727
  .. .. ..$ Number  : chr "41176"
  .. .. ..$ Theme   : chr "Elves"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "The Secret Market Place"
  .. .. ..$ Pieces  : int 691
  .. .. ..$ USPrice : num 60
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41176-1.jpg"
  .. .. ..$ Quantity: num 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24957
  .. .. ..$ Number  : chr "71309"
  .. .. ..$ Theme   : chr "Bionicle"
  .. .. ..$ Subtheme: chr "Toa"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Onua - Uniter of Earth"
  .. .. ..$ Pieces  : int 143
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/71309-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24798
  .. .. ..$ Number  : chr "75140"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "The Force Awakens"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Resistance Troop Transporter"
  .. .. ..$ Pieces  : int 646
  .. .. ..$ USPrice : num 70
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75140-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Daianaira"
  ..$ last_name   : chr "Joseph"
  ..$ age         : num 26
  ..$ phone_number: chr "714-555-9762"
  ..$ hobbies     : chr [1:2] "Cooking" "Amateur geology"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25594
  .. .. ..$ Number  : chr "71011"
  .. .. ..$ Theme   : chr "Collectable Minifigures"
  .. .. ..$ Subtheme: chr "Series 15"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "LEGO Minifigures - Series 15 - Sealed Box"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 3.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/71011-18.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 26058
  .. .. ..$ Number  : chr "5005059"
  .. .. ..$ Theme   : chr "Gear"
  .. .. ..$ Subtheme: chr "Video Games/PS3"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Marvel Avengers PS3 Video Game"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 50
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/5005059-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Sean"
  ..$ last_name   : chr "Cordova"
  ..$ age         : num 43
  ..$ phone_number: chr "881-555-7280"
  ..$ hobbies     : chr [1:2] "Origami" "Scouting"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25004
  .. .. ..$ Number  : chr "41565"
  .. .. ..$ Theme   : chr "Mixels"
  .. .. ..$ Subtheme: chr "Series 8"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Hydro"
  .. .. ..$ Pieces  : int 70
  .. .. ..$ USPrice : num 4.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41565-1.jpg"
  .. .. ..$ Quantity: num 5
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25656
  .. .. ..$ Number  : chr "10804"
  .. .. ..$ Theme   : chr "Duplo"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Jungle"
  .. .. ..$ Pieces  : int 86
  .. .. ..$ USPrice : num 50
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/10804-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Amber"
  ..$ last_name   : chr "Terwilliger"
  ..$ age         : num 35
  ..$ phone_number: chr "626-555-5321"
  ..$ hobbies     : chr "Surfing"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24733
  .. .. ..$ Number  : chr "41118"
  .. .. ..$ Theme   : chr "Friends"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Heartlake Supermarket"
  .. .. ..$ Pieces  : int 313
  .. .. ..$ USPrice : num 30
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41118-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25611
  .. .. ..$ Number  : chr "21127"
  .. .. ..$ Theme   : chr "Minecraft"
  .. .. ..$ Subtheme: chr "Minifig-scale"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "The Fortress"
  .. .. ..$ Pieces  : int NA
  .. .. ..$ USPrice : num 110
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/21127-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Katie"
  ..$ last_name   : chr "Evering"
  ..$ age         : num 37
  ..$ phone_number: chr "882-555-7296"
  ..$ hobbies     : chr(0) 
  ..$ purchases   :List of 4
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24659
  .. .. ..$ Number  : chr "71228"
  .. .. ..$ Theme   : chr "Dimensions"
  .. .. ..$ Subtheme: chr "Level Pack"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Level Pack: Ghostbusters"
  .. .. ..$ Pieces  : int 115
  .. .. ..$ USPrice : num 30
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/71228-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 26040
  .. .. ..$ Number  : chr "41579"
  .. .. ..$ Theme   : chr "Mixels"
  .. .. ..$ Subtheme: chr "Series 9"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Camsta"
  .. .. ..$ Pieces  : int 62
  .. .. ..$ USPrice : num 4.99
  .. .. ..$ ImageURL: chr ""
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25659
  .. .. ..$ Number  : chr "75821"
  .. .. ..$ Theme   : chr "The Angry Birds Movie"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Piggy Car Escape"
  .. .. ..$ Pieces  : int 74
  .. .. ..$ USPrice : num 13
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75821-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24765
  .. .. ..$ Number  : chr "70332"
  .. .. ..$ Theme   : chr "Nexo Knights"
  .. .. ..$ Subtheme: chr "Ultimate"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Ultimate Aaron"
  .. .. ..$ Pieces  : int 82
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70332-1.jpg"
  .. .. ..$ Quantity: num 2
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Nerea"
  ..$ last_name   : chr "Feldman"
  ..$ age         : num 28
  ..$ phone_number: chr "423-555-9631"
  ..$ hobbies     : chr(0) 
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24805
  .. .. ..$ Number  : chr "42049"
  .. .. ..$ Theme   : chr "Technic"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Mine Loader"
  .. .. ..$ Pieces  : int 476
  .. .. ..$ USPrice : num 50
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/42049-1.jpg"
  .. .. ..$ Quantity: num 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25921
  .. .. ..$ Number  : chr "75157"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "Rebels"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Captain Rex's AT-TE"
  .. .. ..$ Pieces  : int 972
  .. .. ..$ USPrice : num 120
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75157-1.jpg"
  .. .. ..$ Quantity: num 2
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Julianna"
  ..$ last_name   : chr "Stephens"
  ..$ age         : num 34
  ..$ phone_number: chr "403-555-9991"
  ..$ hobbies     : chr [1:2] "Trainspotting" "Homebrewing"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24692
  .. .. ..$ Number  : chr "31044"
  .. .. ..$ Theme   : chr "Creator"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Park Animals"
  .. .. ..$ Pieces  : int 202
  .. .. ..$ USPrice : num 15
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/31044-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24797
  .. .. ..$ Number  : chr "75138"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "Episode V"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Hoth Attack"
  .. .. ..$ Pieces  : int 233
  .. .. ..$ USPrice : num 25
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75138-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Female"
  ..$ first_name  : chr "Katrina"
  ..$ last_name   : chr "Clyman"
  ..$ age         : num 32
  ..$ phone_number: chr "604-555-3882"
  ..$ hobbies     : chr(0) 
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24689
  .. .. ..$ Number  : chr "60129"
  .. .. ..$ Theme   : chr "City"
  .. .. ..$ Subtheme: chr "Police"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Police Patrol Boat"
  .. .. ..$ Pieces  : int 200
  .. .. ..$ USPrice : num 50
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/60129-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24663
  .. .. ..$ Number  : chr "21027"
  .. .. ..$ Theme   : chr "Architecture"
  .. .. ..$ Subtheme: chr "Skylines"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Berlin"
  .. .. ..$ Pieces  : int 289
  .. .. ..$ USPrice : num 30
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/21027-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 6
  ..$ gender    : chr "Male"
  ..$ first_name: chr "Ramon"
  ..$ last_name : chr "Walker-Reese"
  ..$ age       : num 23
  ..$ hobbies   : chr [1:2] "Basketball" "Videophilia"
  ..$ purchases :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24796
  .. .. ..$ Number  : chr "75137"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "Episode V"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Carbon-Freezing Chamber"
  .. .. ..$ Pieces  : int 231
  .. .. ..$ USPrice : num 25
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75137-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25633
  .. .. ..$ Number  : chr "70318"
  .. .. ..$ Theme   : chr "Nexo Knights"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "The Glob Lobber"
  .. .. ..$ Pieces  : int 95
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70318-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Brandon"
  ..$ last_name   : chr "Lopez"
  ..$ age         : num 21
  ..$ phone_number: chr "606-555-3903"
  ..$ hobbies     : chr "Tour skating"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24713
  .. .. ..$ Number  : chr "10809"
  .. .. ..$ Theme   : chr "Duplo"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Police Patrol"
  .. .. ..$ Pieces  : int 15
  .. .. ..$ USPrice : num 15
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/10809-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24660
  .. .. ..$ Number  : chr "71241"
  .. .. ..$ Theme   : chr "Dimensions"
  .. .. ..$ Subtheme: chr "Fun Pack"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Fun Pack: Slimer"
  .. .. ..$ Pieces  : int 33
  .. .. ..$ USPrice : num 15
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/71241-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Sagi"
  ..$ last_name   : chr "Heredia"
  ..$ age         : num 19
  ..$ phone_number: chr "989-555-3671"
  ..$ hobbies     : chr [1:2] "Rappelling" "Gunsmithing"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24898
  .. .. ..$ Number  : chr "41113"
  .. .. ..$ Theme   : chr "Friends"
  .. .. ..$ Subtheme: chr "Party"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Party Gift Shop"
  .. .. ..$ Pieces  : int 52
  .. .. ..$ USPrice : num 4.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41113-1.jpg"
  .. .. ..$ Quantity: num 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25640
  .. .. ..$ Number  : chr "70325"
  .. .. ..$ Theme   : chr "Nexo Knights"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Infernox captures the Queen"
  .. .. ..$ Pieces  : int 253
  .. .. ..$ USPrice : num 25
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70325-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Michael"
  ..$ last_name   : chr "Cruz"
  ..$ age         : num 17
  ..$ phone_number: chr "361-555-8212"
  ..$ hobbies     : chr "Stone skipping"
  ..$ purchases   :List of 3
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24723
  .. .. ..$ Number  : chr "41172"
  .. .. ..$ Theme   : chr "Elves"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "The Water Dragon Adventure"
  .. .. ..$ Pieces  : int 212
  .. .. ..$ USPrice : num 20
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41172-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24618
  .. .. ..$ Number  : chr "71238"
  .. .. ..$ Theme   : chr "Dimensions"
  .. .. ..$ Subtheme: chr "Fun Pack"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Fun Pack: Cyberman"
  .. .. ..$ Pieces  : int 40
  .. .. ..$ USPrice : num 15
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/71238-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24920
  .. .. ..$ Number  : chr "70605"
  .. .. ..$ Theme   : chr "Ninjago"
  .. .. ..$ Subtheme: chr "Skybound"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Misfortune's Keep"
  .. .. ..$ Pieces  : int 754
  .. .. ..$ USPrice : num 80
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/70605-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 6
  ..$ gender    : chr "Female"
  ..$ first_name: chr "Melissa"
  ..$ last_name : chr "Holmberg"
  ..$ age       : num 36
  ..$ hobbies   : chr [1:2] "Sketching" "Metal detecting"
  ..$ purchases :List of 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24791
  .. .. ..$ Number  : chr "75132"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "The Force Awakens"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "First Order Battle Pack"
  .. .. ..$ Pieces  : int 88
  .. .. ..$ USPrice : num 13
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75132-1.jpg"
  .. .. ..$ Quantity: num 1
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Cody"
  ..$ last_name   : chr "Gonzales"
  ..$ age         : num 44
  ..$ phone_number: chr "973-555-3236"
  ..$ hobbies     : chr "Metalworking"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24908
  .. .. ..$ Number  : chr "42052"
  .. .. ..$ Theme   : chr "Technic"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Heavy Lift Helicopter"
  .. .. ..$ Pieces  : int 1042
  .. .. ..$ USPrice : num 140
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/42052-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 25922
  .. .. ..$ Number  : chr "75149"
  .. .. ..$ Theme   : chr "Star Wars"
  .. .. ..$ Subtheme: chr "The Force Awakens"
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Resistance X-wing Fighter"
  .. .. ..$ Pieces  : int 740
  .. .. ..$ USPrice : num 80
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/75149-1.jpg"
  .. .. ..$ Quantity: num 3
 $ :List of 7
  ..$ gender      : chr "Male"
  ..$ first_name  : chr "Jessie"
  ..$ last_name   : chr "Barron"
  ..$ age         : num 37
  ..$ phone_number: chr "918-555-7552"
  ..$ hobbies     : chr [1:3] "Skateboarding" "Roller derby" "Kombucha Brewing"
  ..$ purchases   :List of 2
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24696
  .. .. ..$ Number  : chr "31050"
  .. .. ..$ Theme   : chr "Creator"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Corner Deli"
  .. .. ..$ Pieces  : int 467
  .. .. ..$ USPrice : num 40
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/31050-1.jpg"
  .. .. ..$ Quantity: num 1
  .. ..$ :List of 10
  .. .. ..$ SetID   : int 24730
  .. .. ..$ Number  : chr "41115"
  .. .. ..$ Theme   : chr "Friends"
  .. .. ..$ Subtheme: chr ""
  .. .. ..$ Year    : int 2016
  .. .. ..$ Name    : chr "Emma's Creative Workshop"
  .. .. ..$ Pieces  : int 108
  .. .. ..$ USPrice : num 9.99
  .. .. ..$ ImageURL: chr "http://images.brickset.com/sets/images/41115-1.jpg"
  .. .. ..$ Quantity: num 1
  [list output truncated]