---
title: "Weeks 3-4"
author: "Ezinne Nwankwo"
date: "5/28/2019"
output: html_document
---


```{r libraries}

library(dplyr)
library(purrr)
library(tidyverse)
library(ggplot2)
#install.packages("repurrrsive")
library(repurrrsive)

```

## Exercise 1 

How many flights to Los Angeles (LAX) did each of the legacy carriers (AA, UA, DL or US) have in May from JFK, and what was their average duration?

```{r}


#install.packages("nycflights13")
library(nycflights13)

flights %>% filter(dest == "LAX") %>%
  filter(origin == "JFK") %>% 
  filter(month == 5) %>% 
  filter(carrier %in% c("AA","UA","DL","US")) %>% 
  group_by(carrier) %>% 
  summarise(
    n = n(), 
    avg_dur = mean(air_time, na.rm = TRUE)
  )

```


## Exercise 2 

What was the shortest flight out of each airport in terms of distance? In terms of duration?

```{r}

#distance
flights %>% 
  group_by(origin) %>%
  filter(distance == min(distance))%>%
  select(origin, dest, carrier, distance) %>%
  arrange(origin, distance) %>% 
  distinct()

#duration
flights %>% 
  group_by(origin) %>%
  filter(air_time == min(air_time, na.rm = TRUE))%>%
  select(origin, dest, carrier, air_time) %>%
  arrange(origin, air_time) %>% 
  distinct()

```



## Exercise 3


Which plane (check the tail number) flew out of each New York airport the most?


```{r}

flights %>% 
  group_by(origin, tailnum) %>% 
  filter(!is.na(tailnum)) %>%
  summarise(n = n()) %>% 
  filter(n == max(n))

```



## Exercise 4 

Which date should you fly on if you want to have the lowest possible average departure delay? What about arrival delay?


```{r}

## lowest avg departure delay
flights %>% 
  mutate(date = paste(year, month, day, sep="/")) %>%
  group_by(date) %>%
  mutate(dep_delay = ifelse(dep_delay < 0, 0, dep_delay)) %>%
  summarize(
    avg_dep_delay = mean(dep_delay, na.rm = TRUE)
  ) %>%
  filter(avg_dep_delay == min(avg_dep_delay))

## arrival delay 
flights %>% 
  mutate(date = paste(year, month, day, sep="/")) %>%
  group_by(date) %>%
  mutate(arr_delay = ifelse(arr_delay < 0, 0, arr_delay)) %>%
  summarize(
    avg_arr_delay = mean(arr_delay, na.rm = TRUE)
  ) %>%
  filter(avg_arr_delay == min(avg_arr_delay))
  

```



## Exercise 5

The line data set is an example included in the coda package containing mcmc posterior samples from a linear regression model. Use tidyr to adjust the data frame such that you can use ggplot2 to create trace plots or dplyr to calculate summary statistics.


```{r}

library(coda)
data(line,package = "coda")
d = as_data_frame(line[["line1"]])


df_tidy <- d %>% 
  mutate(
    iteration = 1:n()
  ) %>%
  gather(parameter, value, -iteration)

df_tidy %>% 
  group_by(parameter) %>% 
  summarise(
    post_mean = mean(value),
    post_med = median(value)
  )


ggplot(df_tidy, aes(x=iteration, y=value, color=parameter)) + 
  geom_line() + 
  facet_wrap(~parameter)


``` 


## Exercsie 6 

Using the sw_people data set in the repurrrsive package, extract the name of all of the characters using: 

- a for loop 
- an apply function 

```{r}

data(sw_people)

sw_for_loop = function() {
  names = c()
  for (i in 1:length(sw_people)){
    names <-c(names, sw_people[[i]]$name)
  } 
  names
}



sw_sapply = function(feature) {
  sapply(sw_people, function(x) x[["feature"]])
}


#install.packages("bench")
bench::mark(
  sw_for_loop(),
  sw_sapply()
)
```


## Exercise 7 

Using the sw_people data set in the repurrrsive package, generate a tidy data frame (tibble) containing as many details as possible.

```{r}

# Viewing Structure
str(sw_people)
View(sw_people)

# Extracting
map_chr(sw_people, "name")

## doesn't work because the films vector can contain one actor in multiple films 
map_chr(sw_people, "films") 

## here we see that the first actor Luke Skywaker is in multiple films 
sw_people[[1]]$films 

## instead do map() so it just puts the results into a list
map(sw_people, "films")[[1]]

all(map_chr(sw_people, 1) == map_chr(sw_people, "name"))

## Creating tidy date frame

data_frame(
  
  name = map_chr(sw_people, "name"),
  height = map_chr(sw_people, "height"), 
  mass = map_chr(sw_people, "mass")
)

## Bad inputs 
sw_people_copy <- sw_people
sw_people_copy[[87]]$mass = NULL 

data_frame(
  
  name = map_chr(sw_people_copy, "name"),
  height = map_chr(sw_people_copy, "height"), 
  mass = map_chr(sw_people_copy, "mass")
)

## can use traceback function to debug after running the function
traceback()

## NAs? 
data_frame(
  
  name = map_chr(sw_people_copy, "name"),
  height = map_chr(sw_people_copy, "height"), 
  mass = map_chr(sw_people_copy, "mass", .default = NA), 
  bad_length = 1:2
)



##Problem: Height and mass are numeric variables but we are reading them in as characters. Sometimes 
##the map_int function doesn't work
data_frame(
  
  name = map_chr(sw_people_copy, "name"),
  height = map_int(sw_people_copy, "height"), 
  mass = map_chr(sw_people_copy, "mass", .default = NA), 
  bad_length = 1:2
)

## so instead try as.integer. When we use view, we see that their are NAs and unknowns

### Bad
data_frame(
  
  name = map_chr(sw_people, "name"),
  height = map_chr(sw_people, "height") %>% as.integer(),
  mass = map_chr(sw_people, "mass")
) %>% View()

### Better 

data_frame(
  
  name = map_chr(sw_people, "name"),
  height = map_chr(sw_people, "height") %>% {ifelse(. == "unknown", NA, .)} %>% 
    as.integer(.),
  mass = map_chr(sw_people, "mass")  %>% {ifelse(. == "unknown", NA, .)} %>% 
    as.integer(.)
) %>% View() 

### Best
### Helper Function to avoid duplicating code

fix_integers <- function(v){
  ifelse(v == "unknown", NA, v) %>% 
    as.integer()
  
}

data_frame(
  
  name = map_chr(sw_people, "name"),
  height = map_chr(sw_people, "height") %>% fix_integers(),
  mass = map_chr(sw_people, "mass")  %>% fix_integers() 
) %>% View() 

## But still getting errors on the mass column 


d = data_frame(
  
  name = map_chr(sw_people, "name"),
  height = map_chr(sw_people, "height") %>% fix_integers(),
  mass = map_chr(sw_people, "mass")  %>% fix_integers() 
) 

##lets see where the problem is 
is.na(d$mass)
map_chr(sw_people, "mass")[is.na(d$mass)]

as.integer("1,358")

##the problem is the commoas so we need to get rid of before we process the data so we must update the fix function

fix_integers <- function(v){
  ifelse(v == "unknown", NA, v) %>% 
    stringr::str_replace_all(",","") %>%
    as.integer()
  
}

data_frame(
  
  name = map_chr(sw_people, "name"),
  height = map_chr(sw_people, "height") %>% fix_integers(),
  mass = map_chr(sw_people, "mass")  %>% fix_integers() 
) %>% View() 


## gender

d = data_frame(
  
  name = map_chr(sw_people, "name"),
  height = map_chr(sw_people, "height") %>% fix_integers(),
  mass = map_chr(sw_people, "mass")  %>% fix_integers(), 
  gender = map_chr(sw_people, "gender")
)

View(d)

unique(d$gender)

## change na?

fix_gender = function(v){
  ifelse(v %in% c("n/a","none"), NA, v)
}

d = data_frame(
  
  name = map_chr(sw_people, "name"),
  height = map_chr(sw_people, "height") %>% fix_integers(),
  mass = map_chr(sw_people, "mass")  %>% fix_integers(), 
  gender = map_chr(sw_people, "gender") %>% fix_gender()
)

View(d)


## dyplr mutate

d = data_frame(
  
  name = map_chr(sw_people, "name"),
  height = map_chr(sw_people, "height"),
  mass = map_chr(sw_people, "mass"), 
  gender = map_chr(sw_people, "gender") 
) %>% 
  mutate(
    height = fix_integers(height),
    mass = fix_integers(mass), 
    gender = fix_gender(gender)
)
    
View(d)

##wesanderson 

wesanderson

##list column 

data_frame(
  movie = names(wesanderson), 
  colors = wesanderson
) %>% 
  arrange(movie)

##but cannot do dplyr operations on a list column
data_frame(
  movie = names(wesanderson), 
  colors = wesanderson
) %>% 
  arrange(color)

##instead we can do this 

data_frame(
  movie = names(wesanderson), 
  colors = wesanderson
) %>% 
  mutate(
    no_colors = map_int(colors, length)
  )

##flatten list columns 

data_frame(
  movie = names(wesanderson), 
  colors = wesanderson
) %>% 
  tidyr::unnest(color = colors) %>% 
  tidyr::nest(color, .key = "colors") ##or go backwards like this but don't do as.data.frame


##Grouping without tidyr

data_frame(
  movie = names(wesanderson), 
  colors = wesanderson
) %>% 
  tidyr::unnest(color = colors) %>% 
  group_by(movie) %>% 
  mutate(
    colors = list(color)
  )

 

```